---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ".",
  fig.path = "man/figures/README-",
  warning = FALSE, 
  message = FALSE,
  fig.width = 5, 
  fig.height = 4
)
```

# pmplots <img align="right" src = "man/figures/metrum_pmplots_git_logo.png" width="135px">

<!-- badges: start -->
<!-- badges: end -->

The goal of pmplots is to create exploratory and diagnostic plots commonly 
used in pharmacometrics.

## Installation

You can install the released version of pmplots from [MPN](https://mpn.metworx.com/docs/) with:

```{r, eval = FALSE}
mpn <- "https://mpn.metworx.com/snapshots/stable/2021-06-20"
install.packages("pmplots", repos = mpn)
```

This installs from a specific, dated snapshot. Please check 
https://mpn.metworx.com/docs/snapshots/ for the most recent snapshot date.

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("metrumresearchgroup/pmplots")
```
## Examples

```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)

data <- pmplots_data_obs()
```


The default pmplots behavior is to expect names following NONMEM convention, 
for exammple `DV` refers to observed values, `PRED` refers to population 
predicted values. With that convention, we can easily make observed versus 
predicted plots

```{r, dv_pred}
dv_pred(data, yname = "MyDrug (ng/ml)")
```

```{r, dv_pred_log}
dv_pred(data, loglog = TRUE)
```


## NPDE plots
```{r, npde_time}
npde_time(data)
```

```{r, npde_pred}
npde_pred(data)
```


## QQ plots
```{r, cwres_q}
cwres_q(data)
```


## Exploratory plots

```{r, cont_cat, fig.height = 5, fig.width = 7}
id <- pmplots_data_id()
cont_cat(id, x = "STUDYc", y = c("WT", "SCR", "AAG")) %>% pm_grid()
```

```{r, pairs, fig.width = 4.5, fig.width = 6}
pairs_plot(id, y = c("WT//Weight (kg)", "SCR//Creat (mg/dL)", "BMI//BMI (kg/m2)"))
```

## Some faceted versions

```{r, facet_example, fig.height = 5, fig.width = 7}
wrap_cont_time(data, y = c("RES","WRES", "CWRES", "NPDE"), ncol = 2)
```


# Function and workflow overview

A functions and features (code + output) listing is available at 
[pmplots_complete.md](https://github.com/metrumresearchgroup/pmplots/blob/master/inst/examples/pmplots_complete.md).  

# Suggested packages

Consider installing the [cowplot](https://CRAN.R-project.org/package=cowplot) 
package to help arranging plots on a page.  Also, consider installing
[latex2exp](https://CRAN.R-project.org/package=latex2exp) to allow you to 
use latex in axis titles.
