---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pmplots <img align="right" src = "man/figures/metrum_pmplots_git_logo.png" width="135px">

<!-- badges: start -->
<!-- badges: end -->

The goal of pmplots is to create exploratory and diagnostic plots commonly 
used in pharmacometrics.

## Installation

You can install the released version of pmplots from [MPN](https://mpn.metworx.com/docs/) with:

```{r, eval = FALSE}
mpn <- "https://mpn.metworx.com/snapshots/stable/2021-06-20"
install.packages("pmplots", repos = mpn)
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("metrumresearchgroup/pmplots")
```
## Example

```{r}
library(pmplots)
data <- pmplots_data_obs()
```


The default pmplots behavior is to expect names following NONMEM convention

```{r}
dv_pred(data)
```





## Function and workflow overview

A functions and features (code + output) listing is available at 
[pmplots_complete.md](https://github.com/metrumresearchgroup/pmplots/blob/master/inst/examples/pmplots_complete.md).  

# Suggested packages

Consider installing the [cowplot](https://CRAN.R-project.org/package=cowplot) 
package to help arranging plots on a page.  Also, consider installing
[latex2exp](https://CRAN.R-project.org/package=latex2exp) to allow you to 
use latex in axis titles.
