--- 
title: "Specifying col//label"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Specifying col//label}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)
```


`col//label` is a way to select the column name in the data set to use
for plotting as well as the label to use for the axis in the plot. This is 
a simple data structure that pmplots parses and uses under the hood. Don't
worry about calling `col_label()` yourself; we'll just use it here to illustrate.

If we want to use weight from the data set and give it a nice name, we can 
use the `col//label` format

```{r}
x <- "WT // Weight (kg)"
```

Here, we've put the column name to the left of  `//` and the axis label name
to the right. pmplots will parse it like this

```{r}
col_label(x)
```

and use the first item to select data from the data frame and the second to 
label your plot. 

If you are making a simple plot and don't want to add an additional label, 
pmplots will just use the column name as the axis label.

```{r}
col_label("WT")
```

You can use alternative separators

```{r}
col_label("WT @@ Weight")
```

You can also include TeX code in the label part which can be utilized in certain
plots

```{r}
col_label("DV // Concentration ($\\mu$g/mL)")
```

Note: you need the latex2exp package installed to make this work. 

In the plot it would look like 

```{r}
dv_pred(pmplots_data_obs(), yname = "Concentration ($\\mu$g/mL)")
```


