---
title: "Customizing Plots"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Customizing Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Set up
```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)

data <- pmplots_data_obs()
```

# A default plot
```{r}
dv_pred(data)
```


## Customize the axis label

```{r}
dv_ipred(data) + labs(x = "Predicted concentration (mg/L)")
```

## Add Greek symbols to an axis label

There are a couple of ways to do this.  The easiest is to have the
[latex2exp](https://CRAN.R-project.org/package=latex2exp) package installed and write the TeX right in the label. 

```{r}
dv_pred(data, x = "IPRED//Predicted concentration ($\\mu$g/mL)")
```

Otherwise, you can trigger R plotmath by putting `!!` at the 
start of the column label

```{r}
dv_pred(data, x = "IPRED//!!'Predicted concentration (' * mu * 'g/mL)'")
```

## Add a run number or other annotation to the plot

```{r}
dv_pred(data) + labs(subtitle = "Run 1001")
```

# Adopt the pmplots look and feel


At some point, you might have to create a plot outside of pmplots, 
but you still want to adopt the pmplots look and feel.  
```{r}
p <- ggplot(data = data, aes(PRED,DV)) + geom_point()
p
```

Use these helpers to style the plot
```{r}
p + pm_theme() + pm_abline() + pm_smooth()
```

