---
title: "Diagnostic Displays"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Diagnostic Displays}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r include = FALSE}
knitr::opts_chunk$set(message = FALSE, fig.align = "center")
```

# Overview

This feature set provides standardized displays of diagnostics, including

- ETA versus covariates
- NPDE or CWRES versus covariates
- NPDE or CWRES diagnostics as 
  - single, comprehensive panel
  - just scatter plots
  - just histogram and QQ plots
- Continuous versus categorical plots

In addition to these standard displays, the user can get an object back 
containing the component plots for the standardized displays 
that you can arrange yourself. 


```{r}
library(pmplots)
data <- pmplots_data_obs()
id <- pmplots_data_id()
cont <- c("WT//Weight (kg)", "AGE//Age (years)")
cat <- c("CPc//Child-Pugh", "STUDYc//Study")
covs <- c(cont,cat)
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V", "ETA3//ETA-KA")
```


# ETA versus covariates

The basic / default behavior is to get a list of arranged plots, one for each 
`ETA`

```{r}
#| fig-width: 6
#| fig-height: 6
p <- eta_covariate(id, x = covs, y = etas)

names(p) 

p$ETA1
```

We can label the panels; thinking about making this the default

```{r}
#| fig-width: 6
#| fig-height: 6
p <- eta_covariate(id, x = covs, y = etas, tag_levels = "A")

p$ETA1
```


We can arrange this by column instead

```{r}
#| fig-width: 6
#| fig-height: 6
p <- eta_covariate(id, x = covs, y = etas, tag_levels = "A", byrow = FALSE)

p$ETA1
```

Or we can group by the covariate rather than the `ETA` using the `transpose` 
argument

```{r}
p <- eta_covariate(id, x = covs, y = etas, tag_levels = "A", transpose = TRUE)

names(p)
```

Now, we have all the `ETAs` for each covariate on the same page
```{r}
#| fig-width: 6
#| fig-height: 6
p$AGE
```

and

```{r}
#| fig-width: 6
#| fig-height: 6
p$CPc
```


We can make a custom arrangement using the `patchwork` arrangement operators

```{r}
#| fig-height: 8
#| fig-width: 6
p <- eta_covariate_list(id, x = covs, y = etas)

with(p$ETA1, (WT / (CPc + STUDYc) / AGE), tag_levels = "A")
```


# Standard NPDE diagnostics

You can get all the `NPDE` diagnostics in a single graphic. This might be too 
much for a report, but could be handy for your model checkout script

```{r}
#| fig-height: 8
#| fig-width: 6
npde_panel(data, tag_levels = "A")
```

or just the histogram and qq plot

```{r}
#| fig-width: 4
#| fig-height: 6
npde_hist_q(data, tag_levels = "A")
```

or just the scatter plots in long format

```{r}
#| fig-height: 8
#| fig-width: 5
npde_scatter(data, tag_levels = "A")
```

or compact format

```{r}
#| fig-width: 6
#| fig-height: 6
npde_scatter(data, tag_levels = "A", compact = TRUE)
```


You can also customize the layout to be whatever you want

```{r}
#| fig-width: 7
#| fig-height: 6
plots <- npde_panel_list(data)

with(plots, time / (hist + q + tad), tag_levels = "A") 
```


There is some customization for the plot axes and titles, including 

- x-axis tick intervals for `time` and `tad`
- x-axis units for `time` and `tad`
- the name for `pred`

```{r}
#| fig-width: 5
#| fig-height: 7
npde_scatter(
  data, 
  xby_tad = 12, 
  xby_time = 48,
  xname = "concentration", 
  tag_levels = 1
)
```

# NPDE versus covariates

This works like `eta_covariate()`

```{r}
#| fig-width: 6
#| fig-height: 7
npde_covariate(data, covs, tag_levels = "a", byrow = FALSE)
```

```{r}
#| fig-width: 6
#| fig-height: 7
plots <- npde_covariate_list(data, covs)

names(plots)

with(plots, (AGE + WT) / CPc / STUDYc, tag_levels = "i")
```


# Standard CWRES diagnostics

The behavior / feature set looks just like the `NPDE` plots for both 
standard diagnostics and covariates. 


```{r}
#| fig-width: 6
#| fig-height: 6
cwres_scatter(data, tag_levels = "A", compact = TRUE)
```

# Continuous versus categorical panels

These plots work a lot like `eta_covariate()` in that you need to pass in 
both the `x` and `y` variables. 

```{r}
cont <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", "HT//Height (cm)")
cat <- c("CPc//Child-Pugh", "STUDYc//Study", "RF//Renal function", "TALL//Tall")
id$TALL <- factor(id$HT > 180, labels = c("No", "Yes"))
```

```{r}
cont_cat_panel(id, x = cat, y = cont)
```

