---
title: "ETA Plots"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{ETA Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Set up
```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)

data <- pmplots_data_id()
```


A good workflow is to create a character vector of your etas and 
their names.  
```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-VC", "ETA3//ETA-KA")

etas
```


Note that very frequently, ETA plots come back as a list of plots, 
one for each ETA.  In our examples, we'll use the cowplot package to 
arrange the plots into a grid.  

We'll make a special version of `plot_grid` that will make the piping 
a little smoother

```{r, message = FALSE, warning = FALSE}
library(cowplot)

grid_plot <- function(x) plot_grid(plotlist=x)
```


# ETA histogram
```{r}
eta_hist(data,etas) %>% grid_plot()
```




# ETA Pairs
```{r}
eta_pairs(data,etas)
```

# ETA versus categorical variable
```{r}
eta_cat(data, x = "STUDYc", y = etas) %>% grid_plot()
```
