---
title: "Vectorized Plots"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vectorized Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Set up
```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)

data <- pmplots_data_obs()
```


# Vectorized plots

Some pmplots functions have been vectorized so that you can pass in 
a vector of inputs and get a list of plots back.  This is a convenience 
feature that allows you to quickly make several plots.  The intended use
is to arrange those plots in a single page or multiple pages for display.

For example, we can plot `WRES` versus `WT`
```{r}
wres_cont(data, x = "WT")
```

If we wanted to vectorize this plot and look at `WRES` versus
`WT`, `ALB`, `CRCL`, and `AST` we would write

```{r}
wres_cont(data, x = c("WT", "ALB", "CRCL", "AST"))
```

And we get a list of plots back.  This list can be arranged on the fly with
```{r}
covs <- c(
  "WT//Weight (kg)", "ALB//Albumin", 
  "CRCL//Creatinine clearance", "AST//Aspartate aminotransferase"
)

wres_cont(data, x = covs) %>% pm_grid()
```


In this example, we also made the vector of inputs full `col_label` specification.

Another example are the `eta_cont` plots

```{r}
id <- pmplots_data_id()


eta_cont(data, x = covs, y = "ETA1//ETA-CL") %>% pm_grid()
```



# What plots are vectorized?

Basically any plot where the user is required to identify the column 
for plotting.  So in the example, `wres_cont` asks the user to specify 
what the continuous variable is for the x-axis.  This plot is vectorized. 
Same with `wres_cat`

```{r}
wres_cat(data, x = c("STUDYc", "CPc")) %>% pm_grid()
```


In contrast, `dv_pred` is hard-wired to look for `DV` and `PRED`.  It is 
designed to look for only one thing on each axis.  This plot is not vectorized.

You can use `pm_scatter_list` _as_ a vectorized function to vectorize
anything.  So this allows us to do

```{r}
pm_scatter_list(data, y  = "WRES", x = c("PRED", "IPRED", "TIME")) %>% pm_grid()
```

Or just use `lapply` or  `purrr::map`

```{r}
lapply(c("PRED", "IPRED", "TIME"), wres_cont, df = data, y = "WRES") %>% pm_grid()
```



Please see the help topic for each function to know if that 
function is vectorized or not.  


