---
title: "pmplots"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{pmplots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Set up
```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)
```

# Example data

There is an example data set embedded in pmplots
```{r}
data <- pmplots_data_obs()
```

pmplots is designed to work with data sets that have columns named according
to certain expectations.  So we tend to look for these types of columns
```{r}
select(data, ID, TIME, DV, IPRED, ETA1, CWRESI)
```

You might already have NONMEM modeling results with these column names. When
the data set has these names, pmplots will work more automatically with 
the data set, requiring less manual input from the user.

Other columns that we have in the examples can be named according to 
your choosing

```{r}
select(data, WT, ALB, STUDY, STUDYc, CRCL)
```


# Your first plot

With the data setup like this, we can make a plot of DV versus PRED
very easily

```{r}
dv_pred(data)
```

This plots `dv` versus `pred` and the name of the function indicates
what will come out.  pmplots can make this plot because there are columns
called `DV` and `PRED` in the data set

```{r}
select(data, DV, PRED)
```

The overall philosophy of the package is to pass in data with these
expected column names and receive a plot back.  We will see how we can 
customize some aspects of the plots.  But overall, the idea is that the 
function determines the look and feel of the plot.  If you find yourself 
wanting a lot of creative customization then the suggestion is to 
work with plain old ggplot2 to make the plot

# Other plots
There are a lot of plotting functions in pmplots, but the naming is systematic
so that you can know the output from the name. 

Similarly, 

```{r}
cwresi_time(data)
```

gives you conditional weighted residuals versus time. 


And you can get different types of histogram plots
```{r}
cwresi_hist(data)
```

# Specifying data and axis title

Let's look at `cwresi_time` function and look at the basic inputs
for the plot

```{r}
formals(cwresi_time)[1:3]
```

The first argument is `df` , the data set in data.frame format. The second 
argument is `x` or what goes on the x-axis, and third `y`, what goes on 
the `y` axis.  The defaults for these arguments are the output from internal 
pmplots functions

```{r}
pmplots:::pm_axis_time()
```

```{r}
pmplots:::pm_axis_cwresi()
```

For `x`, we have the name of the column in the data set (`TIME`) followed 
by a double-front-slash (`//`) and then the name that we want to go on 
the x-axis (`Time`).  Similarly for y, the data is in column `CWRESI` and 
we want the y-axis title to be `Conditional weighted residual`. 

This is called `col_label` format, and is a simple way to pass in both pieces 
of data. 

If we wanted to modify either the data column name or the name 
of the axis title, simply provide a replacement for the default

```{r}
cwresi_time(data, y = "CWRESI//Some other axis title")
```

And if you omit the title from the `col_label`, the title will be the column 
name
```{r}
cwresi_time(data, y = "CWRESI")
```


Notice that the `x` argument had another piece in it ... `{xunit}`
```{r}
pmplots:::pm_axis_time()
```

Looking at the `y_time` help topic, we see that `xunit` is the 
time unit for these plots.  So, if our data has time unit 
of days, we can change that aspect of the plot
```{r}
cwresi_time(data, xunit = "days")
```









