---
title: "Wrapped / Faceted Plots"
author: "Kyle Baron"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette: 
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Set up
```{r, message = FALSE, warning = FALSE}
library(pmplots)
library(dplyr)
```

# Example data

There is are example data sets embedded in pmplots
```{r}
data <- pmplots_data_obs()
id <- pmplots_data_id()
```

# Rationale

For most applications, pmplots does not reshape your data frame; it works with 
what you pass in.  However, for some applications, it is convenient to have a 
diagnostic plot that is faceted by a categorical variable in the data set.  This 
vignette demostrates the faceted plots that are available.  This faceting support
is for a focused set of plots only.  Users should generally either create facets 
own or use the `split_plot` function for other applications.


# Plots

## `wrap_res_time`

Enter a vector of column names (or `col_label`) for the 
y argument

```{r}
wrap_res_time(data, y = c("CWRESI", "WRES"))
```


## `wrap_eta_cont`

Here, enter a vector for the x argument
```{r}
wrap_eta_cont(
  id, 
  x = c("WT//WT (kg)", "BMI//BMI (kg/m2)", "ALB//ALB (g/dL)"), 
  y = "ETA1//ETA-CL", 
  scales="free_x", 
  use_labels=TRUE
)
```

In this example, we enter labels along with column names and request that 
the labels be used for the shingle.

We can facet on x or y

```{r}
wrap_eta_cont(
  id, 
  x = "WT", 
  y = c("ETA1", "ETA2", "ETA3"),
  scales="free_x"
)
```


## `wrap_hist`

Create a histogram with vector x column names

```{r}
wrap_hist(data, x = c("CWRESI", "WRES"))
```

## DV vs pred and DV vs ipred
```{r}
wrap_dv_preds(data, yname = "MRG1557")
```

