---
title: ""
output: pdf_document
---

# Introduction

`pmplots` is an `R` package to generate exploratory and diagnostic
plots commonly of interest in pharamcometrics.  Each function in `pmplots`
is named according to the specific plot it generates via calls to functions
in the `ggplot2` `R` package.  

This document lists the functional requirements for the `pmplots` package. 

# Requirements for pharamcometric plotting package `pmplots`
```{r,echo = FALSE, message = FALSE}
library(yaml)
library(kableExtra)
library(pander)
library(dplyr)

x <- yaml.load_file("spec.yml")

handles <- names(x)

x <- lapply(seq_along(handles), function(i) {
  handle <- handles[i]
  data_frame(
    i  = i,
    handle  = handle,
    sec = x[[i]]$section,
    req = x[[i]]$requirements
  )
})
x <- bind_rows(x)

x <- mutate(x, rid = 1:n())
x <- select(x, Section = sec, RID = rid, Requirement = req)

x <- mutate(x, Section = paste0("__", Section, "__"))
x <- mutate(x, Section = if_else(duplicated(Section), "", Section))
#names(x)[1] <- paste0("Section",paste(rep("&nbsp;",6),collapse=""))
#x <- rename(x,`Section header&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;` = Section)
```

```{r, echo  = FALSE}
pander(x, justify = c("left","right", "left"), style = "multiline", 
       split.cells = c(10, 3, 40), split.tables = 100)
```







