---
title: "Vectorized Plotting Functions"
output: 
  github_document:
    toc: true
---

```{r}
knitr::opts_chunk$set(fig.path = "img/vectorized-", 
                      comment = '.', fig.width = 5, fig.height = 5)
```


```{r, message = FALSE}
library(pmplots)
library(mrggsave)
library(dplyr)
data <- pmplots_data_obs()
id <- pmplots_data_id()
```


# Most functions are not vectorized

In this example, we just get back a single ggplot object

```{r}
dv_time(data)
```


# But some functions are vectorized
```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V", "ETA3//ETA-KA")
x <- eta_hist(data, etas)
```

```{r}
is.list(x)
```
```{r}
x[[2]]
```

## `eta_hist` is vectorized 
This function is vectorized because it takes a vector of 
eta indicators and returns a list of plots.

# Now more functions are vectorized

## Vectorize over x-values

For example, this is vectorized over the x values
```{r}
covs <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", 
          "CRCL//Creat Clearance (ml/min)")

eta_cont(data, x = covs, y = etas[1]) %>% 
  mrggdraw(ncol = 2)
          
```

## Vectorize over y-values

We can also vectorize over the y values

```{r}
eta_cont(data, x = covs[2], y = etas) %>%
  mrggdraw(ncol = 2)
```

## Vectorize over x-values and y-values

First, the loop is across the x values, then 
the loop is across the y values

```{r, fig.width = 8, fig.height = 8}
eta_cont(data, x = covs, y = etas) %>%
  mrggdraw(ncol = 3)
```




