---
title: "Available functions"
author: ""
date: ""
output:
  github_document:
    toc: true
---

```{r, echo=FALSE}
knitr::opts_chunk$set(comment='.', message=FALSE, warning=FALSE,
                      fig.path="img/everyfunction--",
                      fig.width=4, fig.height=4)
```


```{r}
library(pmplots)
library(dplyr)
library(mrggsave)
library(purrr)
```


# Example data in the package
```{r global}
df <- pmplots_data_obs() %>% mutate(CWRES = CWRESI)

id <- pmplots_data_id()

dayx <- defx(breaks = seq(0,168,24))

.yname <- "MRG1557 (ng/mL)"

etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")

covs <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", "SCR//Creatinine (mg/dL)")

```

Override the `df` and `id` objects in the above chunk
```{r}
## Nothing here
```


# `col//title` specification

This is a way to specify the column name for source
data along with the axis label

```{r}
col_label("CL//Clearance (L)")
```

When only the column is given, then the column name will be 
used for the column title:

```{r}
col_label("WT")
```


## Fill in `CWRES` if it doesn't exist
```{r}
dat <- mutate(df, CWRES = NULL)

cwresi_time(df)

cwres_time(dat)
```



# Observed vs predicted

## Observed versus population predicted (`dv_pred`)

```{r}
dv_pred(df, yname = .yname)
```

### Observed versus population predicted - log/log
```{r}
dv_pred(df, loglog=TRUE, yname = .yname)
```

## Observed versus individual predicted (`dv_ipred`)
```{r}
dv_ipred(df, yname=.yname)
```

### Observed versus individual predicted - log/log
```{r}
dv_ipred(df, loglog=TRUE, yname = .yname)
```

### Observed versus both PRED and IPRED
```{r, fig.width = 6}
dv_preds(df) %>% pm_grid(ncol=2)
```



# Residual plots

## Residuals

### Residuals versus time (`res_time`)
```{r}
res_time(df)
```

### Residuals versus time after first dose (`res_tafd`)
```{r}
res_tafd(df)
```


### Residuals versus time after dose (`res_tad`)
```{r}
res_tad(df)
```

### Residuals versus population predicted (`res_pred`)
```{r}
res_pred(df)
```

### RES versus continuous covariate (`res_cont`)

```{r}
res_cont(df, x="WT//Weight (kg)")
```

This function is also vectorized in x.

```{r, fig.height = 6, fig.width = 6}
c("WT", "CRCL", "AST") %>% map(.f = partial(res_cont,df)) %>% pm_grid()
```


### RES by categorical covariate (`res_cat`)
```{r}
dplyr::count(df, STUDYc)
res_cat(df, x="STUDYc//Study type")
```

### Residual histogram (`res_hist`)

```{r}
res_hist(df)
```


## Weighted residuals

### Weighted residuals versus time (`wres_time`)
```{r}
wres_time(df) 
```

### Weighted residuals versus time after first dose (`wres_tafd`)
```{r}
wres_tafd(df)
```


### Weighted residuals versus time after dose (`wres_tad`)
```{r}
wres_tad(df)
```

### Weighted esiduals versus population predicted (`wres_pred`)
```{r}
wres_pred(df)
```

### WRES versus continuous covariate (`wres_cont`)

This function is also vectorized in x.

```{r}
wres_cont(df, x="WT//Weight (kg)")
```

### WRES by categorical covariate (`wres_cat`)
```{r}
wres_cat(df, x="STUDYc//Study type")
```

### Weighted residual histogram (`wres_hist`)
```{r}
wres_hist(df)
```

### WRES QQ plot (`wres_q`)
```{r}
wres_q(df)
```


## Conditional weighted residuals (CWRES)

### CWRES versus time (`cwres_time`)
```{r}
cwres_time(df)
```


### Conditional weighted residuals versus time after first dose (`cwres_tafd`)
```{r}
cwres_tafd(df)
```


### CWRES versus time after dose (`cwres_tad`)
```{r}
cwres_tad(df)
```

### CWRES versus continuous covariate (`cwres_cont`)
```{r}
cwres_cont(df, x="WT//Weight (kg)")
```

Vectorized version
```{r, fig.height = 6, fig.width = 6}
cwres_cont(df, covs) %>%  pm_grid(ncol=2)
```


### CWRES by categorical covariate (`cwres_cat`)
```{r}
cwres_cat(df, x="STUDYc//Study type")
```

```{r}
cwres_cat(df, x="STUDYc//Study type", shown=FALSE)
```

Vectorized version

```{r}
cwres_cat(df, x = c("STUDYc//Study", "RF//Renal Function"))
```


### Conditional weighted residual histogram (`cwres_hist`)
```{r}
cwres_hist(df)
```

### CWRES versus population predicted (`cwres_pred`)
```{r}
cwres_pred(df)
```

### CWRES QQ plot (`cwres_q`)
```{r}
cwres_q(df)
```


# NPDE plots

## NPDE versus TIME (`npde_time`, `npde_tad`, `npde_tafd`)

```{r}
npde_time(df)
```

## NPDE versus TAD (`npde_tad`)

```{r}
npde_tad(df)
```

## NPDE versus TAFD (`npde_tafd`)

```{r}
npde_tafd(df)
```


## NPDE versus PRED (`npde_pred`)

```{r}
npde_pred(df)
```

## NPDE versus continuous variable (`npde_cont`)

```{r}
npde_cont(df, "WT")
```

## NPDE versus categorical variable (`npde_cat`)

```{r}
npde_cat(df, "STUDYc")
```

## QQ-plot with NPDE (`npde_q`)
```{r}
npde_q(df)
```


## NPDE histogram (`npde_hist`)
```{r}
npde_hist(df)
```


# ETA plots

```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")
covs <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", "SCR//Creatinine (mg/dL)")
```

## ETA versus continuous covariates (`eta_cont`)

### Grouped by eta
```{r, fig.width=6, fig.height=7}
eta_cont(id, x=covs,y=etas[2]) %>% pm_grid()
```

### Grouped by covariate
```{r, fig.width=6, fig.height=7}
eta_cont(id, x=covs[1], y=etas) %>% pm_grid(ncol=2)
```

## ETA by categorical covariates (`eta_cat`)

```{r}
p <- eta_cat(id, x="STUDYc//Study type", y=etas)
```


```{r, fig.width=6, fig.height=7}
pm_grid(p)
```

## ETA histograms (`eta_hist`)


```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")
p <- eta_hist(id,etas, bins=10)
```

```{r,fig.width=6, fig.height=7}
pm_grid(p)
```


## ETA pairs plot (`eta_pairs`)

```{r}
p <- eta_pairs(id,etas)
```


```{r,fig.width=6, fig.height=7}
print(p)
```



# DV versus time (`dv_time`)

## Basic plot

```{r}
dv_time(df, yname = .yname)
```


## Faceted

```{r,fig.width=6, fig.height=7}
dv_time(df, yname="MRG1557 (ng/mL)") + facet_wrap(~DOSE, scales="free_x")
```


__NOTE__ this will not work as you expect; the labels are wrong.  
```{r}
cwres_cat(df, x = "STUDYc") + facet_wrap(~CPc)
```

The only way to get this right is

```{r}
cwres_cat(df, x = "STUDYc", shown=FALSE) + facet_wrap(~CPc)
```


## log-Scale
```{r,fig.width=6, fig.height=6}
dv_time(df, yname="MRG1557 (ng/mL)", log=TRUE) + facet_wrap(~STUDYc)
```


## Wrapped plots

### histogram
```{r}
wrap_hist(df, x = c("WT", "ALB", "SCR"), scales = "free", bins=10, ncol=2)
```

### eta
```{r}
wrap_eta_cont(df, y = "ETA1", x = c("WT", "ALB"), scales="free_x")
```

### DV/PRED, DV/IPRED
```{r, fig.height=7}
wrap_dv_preds(df, ncol=1)
```


### Use labels in the strip
```{r}
wrap_eta_cont(
  df, 
  y = "ETA1", 
  x = c("WT//Weight (kg)", "ALB//Albumin (g/dL)"),
  scales="free_x", 
  use_labels=TRUE
)
```
## Residuals
```{r}
wrap_res_time(df, y = c("RES", "CWRES", "NPDE"), ncol=2)
```



# Data summary

## Continuous variable by categorical variable (`cont_cat`)
```{r}
cont_cat(id, x="STUDYc", y="WT")
```

## General histogram (`cont_hist`)

```{r}
cont_hist(id, x = "WT", bins = 20)
```

## Split and plot (`split_plot`)
```{r}
p <- split_plot(df, sp="STUDYc", fun=dv_ipred)
```

```{r,fig.width=6, fig.height=7}
pm_grid(p)
```


# Some customization

## Greek letters in axis title
```{r}
dv_pred(df, x = "PRED//Concentration ($\\mu$g)")
```


## Modify x-axis

```{r}
a <- list(trans="log", breaks = logbr3())

dv_time(df, xs=a)
```

## Modify y-axis
```{r}
dv_time(df, ys=a, yname="Y-axis name")
```


## Add layers

```{r}
p <- ggplot(df, aes(PRED,DV))  + geom_point() + pm_theme()
```

### smooth
```{r}
layer_s(p)
```

### abline
```{r}
layer_a(p)
```

```{r}
layer_h(cwres_time(df,add_layers=FALSE))
```


## Drop extra layers
```{r}
dv_pred(df, smooth=NULL)
```

```{r}
dv_pred(df, abline=NULL)
```

```{r}
cwres_time(df, hline = NULL)
```


```{r}
dv_pred(df, abline=NULL, smooth = NULL)
```

### Drop all extra layers
```{r}
dv_pred(df, add_layers=FALSE)
```

## Custom breaks

Default breaks:
```{r}
dv_time(df)
```

Break every 3 days
```{r}
dv_time(df, xby=72)
```

Custom breaks and limits
```{r}
a <- list(br = seq(0,240,48), limits=c(0,240))
dv_time(df, xs=a)
```


## Extra reference lines to [C]WRES plots

```{r}
wres_time(df) + geom_3s()
```

# Replicate look and feel

```{r}
p <- ggplot(df, aes(IPRED,DV)) + geom_point()

p
```

## Theme

```{r}
p + pm_theme()
```

### Plain
```{r}
p + theme_plain()
```

## Smooth

```{r}
p + pm_smooth()
```

## Abline

```{r}
p + pm_abline()
```


## Horizontal reference line

```{r}
ggplot(df, aes(TIME,CWRES)) + geom_point() + pm_hline()
```

## Rotate x and y axis labels
```{r}
dv_pred(df) + rot_x(angle = 90) + rot_y()
```

# Standard axis titles

```{r}
pm_axis_time()
pm_axis_tad()
pm_axis_tafd()
pm_axis_res()
pm_axis_wres()
pm_axis_cwres()
pm_axis_npde()
pm_axis_dv()
pm_axis_pred()
pm_axis_ipred()
```

# Log breaks
```{r}
logbr3()
```
```{r}
logbr()
```


