---
title: "Available functions: pmplots"
author: ""
date: ""
output:
  github_document:
    toc: true
params:
  form_only: FALSE
---

# Setup and packages

```{r, echo=FALSE}

knitr::opts_chunk$set(
  comment='.', message=FALSE, warning=FALSE,
  fig.path="img/pmplots_complete--",
  eval = !params$form_only,
  fig.width=4, fig.height=4
)
```


```{r}
library(pmplots)
library(dplyr)
library(purrr)
```

\newpage

# Example data in the package
```{r global}
df <- pmplots_data_obs() %>% mutate(CWRES = CWRESI)

id <- pmplots_data_id()

dayx <- defx(breaks = seq(0,168,24))

.yname <- "MRG1557 (ng/mL)"

etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")

covs <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", "SCR//Creatinine (mg/dL)")

```

Override the `df` and `id` objects in the above chunk
```{r}
## Nothing here
```

\newpage

# `col//title` specification

This is a way to specify the column name for source
data along with the axis label

```{r}
col_label("CL//Clearance (L)")
```

When only the column is given, then the column name will be 
used for the column title:

```{r}
col_label("WT")
```

\newpage

## Fill in `CWRES` if it doesn't exist
```{r, message = TRUE}
dat <- mutate(df, CWRES = NULL)

cwresi_time(df)

cwres_time(dat)
```

\newpage

# Observed vs predicted

## Observed versus population predicted (`dv_pred`)

```{r}
dv_pred(df, yname = .yname)
```

\newpage

## Observed versus population predicted - log/log
```{r}
dv_pred(df, loglog=TRUE, yname = .yname)
```

\newpage

## Observed versus individual predicted (`dv_ipred`)
```{r}
dv_ipred(df, yname=.yname)
```

\newpage

## Observed versus individual predicted - log/log
```{r}
dv_ipred(df, loglog=TRUE, yname = .yname)
```

\newpage

## Observed versus both PRED and IPRED
```{r, fig.width = 6}
dv_preds(df) %>% pm_grid(ncol=2)
```

\newpage

# Residual plots


## Residuals versus time (`res_time`)
```{r}
res_time(df)
```

\newpage

## Residuals versus time after first dose (`res_tafd`)
```{r}
res_tafd(df)
```

\newpage

## Residuals versus time after dose (`res_tad`)
```{r}
res_tad(df)
```

\newpage

## Residuals versus population predicted (`res_pred`)
```{r}
res_pred(df)
```

\newpage

## RES versus continuous covariate (`res_cont`)

```{r}
res_cont(df, x="WT//Weight (kg)")
```

This function is also vectorized in x.

```{r, fig.height = 6, fig.width = 6}
c("WT", "CRCL", "AST") %>% map(.f = partial(res_cont,df)) %>% pm_grid()
```

\newpage

## RES by categorical covariate (`res_cat`)
```{r}
dplyr::count(df, STUDYc)
res_cat(df, x="STUDYc//Study type")
```

\newpage

## Residual histogram (`res_hist`)

```{r}
res_hist(df)
```

\newpage

# Weighted residuals

## Weighted residuals versus time (`wres_time`)
```{r}
wres_time(df) 
```

\newpage

## Weighted residuals versus time after first dose (`wres_tafd`)
```{r}
wres_tafd(df)
```

\newpage

## Weighted residuals versus time after dose (`wres_tad`)
```{r}
wres_tad(df)
```

\newpage

## Weighted esiduals versus population predicted (`wres_pred`)
```{r}
wres_pred(df)
```

\newpage

## WRES versus continuous covariate (`wres_cont`)

This function is also vectorized in x.

```{r}
wres_cont(df, x="WT//Weight (kg)")
```

\newpage

## WRES by categorical covariate (`wres_cat`)
```{r}
wres_cat(df, x="STUDYc//Study type")
```

\newpage

## Weighted residual histogram (`wres_hist`)
```{r}
wres_hist(df)
```

\newpage

## WRES QQ plot (`wres_q`)
```{r}
wres_q(df)
```

\newpage

# Conditional weighted residuals (CWRES)

## CWRES versus time (`cwres_time`)
```{r}
cwres_time(df)
```

\newpage

## Conditional weighted residuals versus time after first dose (`cwres_tafd`)
```{r}
cwres_tafd(df)
```

\newpage

## CWRES versus time after dose (`cwres_tad`)
```{r}
cwres_tad(df)
```

\newpage

## CWRES versus continuous covariate (`cwres_cont`)
```{r}
cwres_cont(df, x="WT//Weight (kg)")
```

Vectorized version
```{r, fig.height = 6, fig.width = 6}
cwres_cont(df, covs) %>%  pm_grid(ncol=2)
```

\newpage

## CWRES by categorical covariate (`cwres_cat`)
```{r}
cwres_cat(df, x="STUDYc//Study type")
```

```{r}
cwres_cat(df, x="STUDYc//Study type", shown=FALSE)
```

Vectorized version

```{r}
cwres_cat(df, x = c("STUDYc//Study", "RF//Renal Function"))
```

\newpage

## Conditional weighted residual histogram (`cwres_hist`)
```{r}
cwres_hist(df)
```

\newpage

## CWRES versus population predicted (`cwres_pred`)
```{r}
cwres_pred(df)
```

\newpage

## CWRES QQ plot (`cwres_q`)
```{r}
cwres_q(df)
```

\newpage

# NPDE plots

## NPDE versus TIME (`npde_time`)

```{r}
npde_time(df)
```

\newpage

## NPDE versus TAD (`npde_tad`)

```{r}
npde_tad(df)
```

\newpage

## NPDE versus TAFD (`npde_tafd`)

```{r}
npde_tafd(df)
```

\newpage

## NPDE versus PRED (`npde_pred`)

```{r}
npde_pred(df)
```

\newpage

## NPDE versus continuous variable (`npde_cont`)

```{r}
npde_cont(df, "WT")
```

\newpage

## NPDE versus categorical variable (`npde_cat`)

```{r}
npde_cat(df, "STUDYc")
```

\newpage

## QQ-plot with NPDE (`npde_q`)
```{r}
npde_q(df)
```

\newpage

## NPDE histogram (`npde_hist`)
```{r}
npde_hist(df)
```

\newpage

# ETA plots

```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")
covs <- c("WT//Weight (kg)", "ALB//Albumin (g/dL)", "SCR//Creatinine (mg/dL)")
```

\newpage

## ETA versus continuous covariates (`eta_cont`)

Grouped by eta
```{r, fig.width=6, fig.height=7}
eta_cont(id, x=covs,y=etas[2]) %>% pm_grid()
```

Grouped by covariate
```{r, fig.width=6, fig.height=7}
eta_cont(id, x=covs[1], y=etas) %>% pm_grid(ncol=2)
```

\newpage

## ETA by categorical covariates (`eta_cat`)

```{r}
p <- eta_cat(id, x="STUDYc//Study type", y=etas)
```

```{r, fig.width=6, fig.height=7}
pm_grid(p)
```

\newpage

## ETA histograms (`eta_hist`)


```{r}
etas <- c("ETA1//ETA-CL", "ETA2//ETA-V2", "ETA3//ETA-KA")
p <- eta_hist(id,etas, bins=10)
```

```{r,fig.width=6, fig.height=7}
pm_grid(p)
```

\newpage

## ETA pairs plot (`eta_pairs`)

```{r}
p <- eta_pairs(id, etas)
```


```{r,fig.width=6, fig.height=7}
print(p)
```

\newpage

# DV versus time (`dv_time`)

## Basic plot

```{r}
dv_time(df, yname = .yname)
```

\newpage

## Faceted

```{r,fig.width=6, fig.height=7}
dv_time(df, yname="MRG1557 (ng/mL)") + facet_wrap(~DOSE, scales="free_x")
```


__NOTE__ this will not work as you expect; the labels are wrong.  
```{r}
cwres_cat(df, x = "STUDYc") + facet_wrap(~CPc)
```

The only way to get this right is

```{r}
cwres_cat(df, x = "STUDYc", shown=FALSE) + facet_wrap(~CPc)
```

\newpage

## log-Scale
```{r,fig.width=6, fig.height=6}
dv_time(df, yname="MRG1557 (ng/mL)", log=TRUE) + facet_wrap(~STUDYc)
```

\newpage

# DV-PRED-IPRED

- This returns a list of plots; we show only one here (the first 9 IDs) 
as an example

```{r, fig.height = 6, fig.width=6}
dd1 <- filter(df, ID <= 15)

dv_pred_ipred(dd1, nrow = 3, ncol = 3, ylab = "Concentration (ng/mL)", log_y=TRUE)
```


\newpage

# Wrapped plots

## histogram
```{r}
wrap_hist(df, x = c("WT", "ALB", "SCR"), scales = "free", bins=10, ncol=2)
```

\newpage

## eta
```{r}
wrap_eta_cont(df, y = "ETA1", x = c("WT", "ALB"), scales="free_x")
```

\newpage

## DV/PRED, DV/IPRED
```{r, fig.height=7}
wrap_dv_preds(df, ncol=1)
```

\newpage

## Use labels in the strip
```{r}
wrap_eta_cont(
  df, 
  y = "ETA1", 
  x = c("WT//Weight (kg)", "ALB//Albumin (g/dL)"),
  scales="free_x", 
  use_labels=TRUE
)
```

\newpage

## Residuals
```{r}
wrap_res_time(df, y = c("RES", "CWRES", "NPDE"), ncol=2)
```

\newpage

# Vectorized plots

```{r}
pm_scatter(df, x = "TIME", y = c("RES", "WRES", "CWRES"))
```



\newpage

# Data summary

## Continuous variable by categorical variable (`cont_cat`)
```{r}
cont_cat(id, x="STUDYc", y="WT")
```

\newpage

## General histogram (`cont_hist`)

```{r}
cont_hist(id, x = "WT", bins = 20)
```

\newpage

## Split and plot (`split_plot`)
```{r}
p <- split_plot(df, sp="STUDYc", fun=dv_ipred)
```

```{r,fig.width=6, fig.height=7}
pm_grid(p)
```

\newpage

# Some customization

## Latex (including Greek letters) in axis title
```{r}
dv_pred(df, x = "PRED//Concentration ($\\mu$g)")
```

\newpage

## Latex in pairs plot

```{r, fig.width=6}
data <- dplyr::tibble(m = rnorm(100), s = rnorm(100), n = rnorm(100))

x <- c("m//$\\mu$", "s//$\\sigma$", "n//$\\nu$")

pairs_plot(data,x)
```

## Latex in wrapped plots

```{r, fig.width=6}
y <- c("WT//Weight (kg)", "BMI//BMI (kg/m$^2$)", "SCR//SCR (g/dL)")

wrap_cont_time(df, y = y, use_labels=TRUE)
```


## Modify x-axis

```{r}
a <- list(trans="log", breaks = logbr3())

dv_time(df, xs=a)
```

\newpage

## Modify y-axis
```{r}
dv_time(df, ys=a, yname="Y-axis name")
```

## Flip coordinates when labels get cramped

If this is too cramped

```{r}
cont_cat(
  id, 
  y = c("WT", "BMI", "ALB", "CRCL"), 
  x = "STUDYc"
) %>% pm_grid()

```

Try this

```{r, fig.height = 5}
cont_cat(
  id, 
  y = c("WT", "BMI", "ALB", "CRCL"), 
  x = "STUDYc"
) %>% map(~.x+coord_flip()) %>% pm_grid()

```


# Add layers

```{r}
p <- ggplot(df, aes(PRED,DV))  + geom_point() + pm_theme()
```

\newpage

## smooth
```{r}
layer_s(p)
```

\newpage

## abline
```{r}
layer_a(p)
```

```{r}
layer_h(cwres_time(df,add_layers=FALSE))
```

\newpage

## Drop extra layers
```{r}
dv_pred(df, smooth=NULL)
```

```{r}
dv_pred(df, abline=NULL)
```

```{r}
cwres_time(df, hline = NULL)
```

```{r}
dv_pred(df, abline=NULL, smooth = NULL)
```

\newpage

## Modify layer specs

For example, change the values of argument for `geom_smooth`

```{r}
cwres_time(df, smooth = list(method = "loess", span = 0.1, se=TRUE))
```


## Drop all extra layers
```{r}
dv_pred(df, add_layers=FALSE)
```

\newpage

# Custom breaks

Default breaks:
```{r}
dv_time(df)
```

\newpage

Break every 3 days
```{r}
dv_time(df, xby=72)
```

\newpage

Custom breaks and limits
```{r}
a <- list(breaks = seq(0,240,48), limits=c(0,240))
dv_time(df, xs=a)
```

\newpage

# Extra reference lines to [C]WRES plots

```{r}
wres_time(df) + geom_3s()
```

\newpage

# Replicate look and feel

```{r}
p <- ggplot(df, aes(IPRED,DV)) + geom_point()

p
```

\newpage

## Theme

```{r}
p + pm_theme()
```

\newpage

## Plain
```{r}
p + theme_plain()
```

\newpage

## Smooth

```{r}
p + pm_smooth()
```

\newpage

## Abline

```{r}
p + pm_abline()
```

\newpage

## Horizontal reference line

```{r}
ggplot(df, aes(TIME,CWRES)) + geom_point() + pm_hline()
```

\newpage

## Rotate x and y axis labels
```{r}
dv_pred(df) + rot_x(angle = 90) + rot_y()
```

\newpage

# Standard axis titles

```{r}
pm_axis_time()
pm_axis_tad()
pm_axis_tafd()
pm_axis_res()
pm_axis_wres()
pm_axis_cwres()
pm_axis_cwresi()
pm_axis_npde()
pm_axis_dv()
pm_axis_pred()
pm_axis_ipred()
```

\newpage

# Log breaks
```{r}
logbr3()
```
```{r}
logbr()
```
